Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-12 paper/main.tex
spacing

\begin{figure*}
\centering
\vspace{-.5cm}
\begin{tabular}{r|c|c|c|c|c}
%
& t08 (modified t08a) & t19 & t30 & t15 & t13\\
%
\hline
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
while (y>x) {
  x++; tick(1);
}
while (x>2) {
  x -= 3; tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
while (i>100) {
  i--; tick(1) }
i += k+50;
while (i>=0) {
  i--; tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
while (x>0) {
  x--;
  t=x, x=y, y=t;
  tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
assert(y>=0);
while (x > y) {
  x -= y+1;
  for (z=y; z>0; z--)
    tick(1);
  tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
  while (x>0) {
    x--;
    if (*) y++;
    else
      while (y>0)
        y--, tick(1);
    tick(1); }
\end{lstlisting}
%
\\
\hline
%
%
%
\toolname
  & {\small $1.33|[x,y]| {+} 0.33 |[0,x]|$ }
  & {\small $50 {+} |\inter {-1} i| {+} |\inter 0 k|$ }
  & {\small $|\inter 0 x| {+} |\inter 0 y|$}
  & {\small $|\inter 0 x|$}
  & {\small $2 |\inter 0 x| {+} |\inter 0 y|$}
\\
%
Rank
  & {\small $2 {+} y {-} x (?)$ }
  & {\small $54+k+i$ }
  & {\small ---}
  & {\small $2+2x-y$ }
  & {\small $0.5{\cdot}y^2 {+} yx \ldots$}
           % +0.5{\cdot}x^2\ldots$} % + 1{-}0.5{\cdot}y){-}0.5{\cdot}x $}
\\
%
{\sc loopus}
&
{\small
  \begin{tabular}{c}
    $\max(0, x{-}2)$\\ $+ 2\max(0, y {-} x)$
  \end{tabular}
}
&
{\small
  \begin{tabular}{c}
    $\max(0, i{-}100)$ \\
    $+ \max(0, k {+} i {+} 51)$
  \end{tabular}
}
&
{\small ---}% $1 + \max(x, y)$ (???)
&
{\small ---}
&
{\small \begin{tabular}{c}
           $2\max(x, 0)$ \\
           $+ \max(y, 0)$
        \end{tabular}}
\end{tabular}
\vspace{.1cm}
\caption{ Comparison of resource bounds derived by different tools on
  several examples with linear bounds.  The output of Rank has been manually
  simplified to fit the table.  }
\label{fig:compar}
\end{figure*}

>>>>

\begin{figure*}
\centering
\vspace{-.5cm}
\begin{tabular}{r|c|c|c|c|c}
%
& t08 (modified t08a) & t19 & t30 & t15 & t13\\
%
\hline
&
\begin{lstlisting}[basicstyle=\tt\footnotesize]
while (y>x) {
  x++; tick(1);
}
while (x>2) {
  x -= 3; tick(1);
}
\end{lstlisting}
&
\hspace{-.5cm}\begin{lstlisting}[basicstyle=\tt\footnotesize]
while (i>100) {
  i--; tick(1) }
i += k+50;
while (i>=0) {
  i--; tick(1);
}
\end{lstlisting}\hspace{-.5cm}
&
\begin{lstlisting}[basicstyle=\tt\footnotesize]
while (x>0) {
  x--;
  t=x, x=y, y=t;
  tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\footnotesize]
assert(y>=0);
while (x > y) {
  x -= y+1;
  for (z=y; z>0; z--)
    tick(1);
  tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\footnotesize]
while (x>0) {
  x--;
  if (*) y++;
  else
    while (y>0)
      y--, tick(1);
  tick(1); }
\end{lstlisting}
%
\\
\hline
%
%
%
\toolname
  & {\small $\!\!\!1.33|[x,y]| {+} 0.33 |[0,x]|\!\!\!$ }
  & {\small $\!\!\!\!\!50 {+} |\inter {-1} i| {+} |\inter 0 k|\!\!\!\!\!\!$ }
  & {\small $|\inter 0 x| {+} |\inter 0 y|$}
  & {\small $|\inter 0 x|$}
  & {\small $2 |\inter 0 x| {+} |\inter 0 y|$}
\\
%
Rank
  & {\small $2 {+} y {-} x (?)$ }
  & {\small $54+k+i$ }
  & {\small ---}
  & {\small $2+2x-y$ }
  & {\small $0.5{\cdot}y^2 {+} yx \ldots$}
           % +0.5{\cdot}x^2\ldots$} % + 1{-}0.5{\cdot}y){-}0.5{\cdot}x $}
\\
%
{\hspace{-.2cm}LOOPUS}
&
{\small
  \begin{tabular}{c}
    $\max(0, x{-}2)$\\ $+ 2\max(0, y {-} x)$
  \end{tabular}
}
&
{\small
  $\!\!\!\!$\begin{tabular}{c}
    $\max(0, i{-}100)$ \\
    $+ \max(0, k {+} i {+} 51)$
  \end{tabular}$\!\!\!\!$
}
&
{\small ---}% $1 + \max(x, y)$ (???)
&
{\small ---}
&
{\small \begin{tabular}{c}
           $2\max(x, 0)$ \\
           $+ \max(y, 0)$
        \end{tabular}}
\end{tabular}
\vspace{.1cm}
\caption{ Comparison of resource bounds derived by different tools on
  several examples with linear bounds.  The output of Rank has been manually
  simplified to fit the table.  }
\label{fig:compar}
\end{figure*}
